MsCcHSFeed Outline

### 2022-09-14 MsCcHSFeedOutlineDec15.Rmd
Added multinomial regression and two-tailed z-test

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
library(lubridate)
library(lmerTest)
```

@@

>>>>

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
library(lubridate)
library(lmerTest)
library(nnet)
library(jmv)
```

@@

Multinomial regression from Katherine to report proportions of outcomes in PHS treatment group

```{r}
datamulti <- data[data$para == "yes" & data$HS == "yes", ]
datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe", "wowe mongo"), labels = c("WE", "Wander", "Small WOWE", "Large WOWE"))
datamulti$food <- factor(datamulti$food, levels = c("TB", "DC"))
```

Use the multinom command to run a model

```{r}
fatemodel <- multinom(fate ~ food, data = datamulti)

summary(fatemodel)
```

Get p-values:

```{r}
fatez <- summary(fatemodel)$coefficients/summary(fatemodel)$standard.errors
#2-tailed z test
pfate <- (1-pnorm(abs(fatez), 0, 1))*2
pfate
```
